Discovering cell type motifs in connectomics data

### 2013-11-30 docs/paper.tex
updates to paper text

@@

\subsection{Validation}
Posterior enumeration tests
extensive synthetic data
Show results in suplementary figures

\subsection {Mouse Retina}
Dense serial electron microscopy of a $VOLUMNE$ in the mouse
retina by \autocite{Helmstaedter2013} yielded a listing of places where
neurons come into contact. There were $number$ cells originally, whcih
were refined through various classification schemes. We selected the
$950$ for which the location of the soma could be reconstruted from
the provided cell plots (soma locations were not provided by the
study's authors in machine-readble form).

The authors were unable to disambiguate actual ``synapses'' in the
full data set, but were able to measure the points of contact between
cells. Thus we don't have ``real'' synapses. We also don't have directionality.

\subsection{C. elegans}
Where do we get the data
what cells

>>>>

We describe three link functions, ``Logistic-distance'',

@@

\subsection{Validation}

\subsection {Mouse Retina}
Dense serial electron microscopy of a $VOLUMNE$ in the mouse retina by
\autocite{Helmstaedter2013} yielded a listing of places where neurons
come into contact. There were $number$ cells originally, and selected
the $950$ for which the location of the soma could be reconstruted
from the provided cell plots (soma locations were not provided by the
study's authors in machine-readble form). Ultimately
this left a matrix between the total synapse-like contact area between
all pairs of 950 cells. Area was thresholded at $0.5\mum$, determined
by hand, to yield a 950 $\times$ 950 entry matrix that served as input
to our algorithm. We measured the distance between cells using
the reconstructed soma centers, and used the Logistic-Distance
spatial relation. Hyperprior distributions are shown in \ref{supplemental}.

We obtained the connectome of c. elegans from \autocite, and isolated
the 279 nonpharyngeal neurons, with a total of 6393 chemical synapses
and 890 gap junctions originally cleaned up in \autocite{Chen2006}. A
cell's position was its distance along the anterior-posterior axis
normalzed between zero and one. We used both networks, the chemical
network as a directed graph and the electrical network as undirected
graph. We use the synapse counts with the logistic-distance poisson
likelihood, scaling the counts by a factor of 4 to compensate for 
the Poisson's underdispersion.
